Initial Analysis

### 2019-08-20 Initial_Analysis.Rmd
Created file to deal with country duplications

## Creating a subset dataset so i can work on my laptop and not remoteley
SubsetData <- TenTwenyfive %>% 
  filter(Name=="USA (East Coast)")

write.csv(SubsetData,
          "SubsetData.csv",
          row.names = F)
```

>>>>

## Creating a subset dataset so i can work on my laptop and not remoteley
SubsetData <- TenTwentyFive %>% 
  filter(Country_Territory=="USA (East Coast)")
